Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Fix typos.
Minor tweaks to text.

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. Second, and more
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
\end{equation}
time steps, where $H_x$ is closed-loop transfer function for the
$x$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.

@@

In general, the $X$-axis positioning requirements are more stringent
for both CS and raster scanning. Due to the step inputs the $X$-axis
must track, we have found that compensating hysteresis and creep to be
particular helpful during $\mu$-path scanning. Thus, the $X$-axis
compensator also includes an inverse creep and hysteresis model. The
hysteresis model is a modified Prandtl-Ishlinskii type model and is
based on the work of \cite{kuhnen_modeling_2003}, while the drift
compensation models the piezo creep as a simple second-order transfer
function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the
hysteresis inversion is indicated by $\mathcal{H}^{-1}[\cdot]$. We
have found that the inclusion of these extra compensators limits the
overshoot of the $X$-axis during larger moves between different
$\mu$-paths (e.g., without them, the $X$-axis trajectory in
Fig.~\ref{fig:with_ff} would show noticeable overshoot). More details
on fitting the creep and hysteresis models can be found in our other
work \cite{braker_afmmpc_2019}.

@@

In principle, one could mitigate these issues with a full MIMO control
design. In this work, we opt for a much simpler feedforward scheme.
For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in
Fig.~\ref{fig:afm_bd_dinv}) with three notches: at 215~Hz, 350~Hz, and 505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the dashed-pink curves and the
resulting overall FRF is shown as the blue curves, which show a
dramatic reduction in the cross coupling. A similar effect could be
achieve by using a simple low-pass filter. However, to achieve the
same 40~dB of attenuation of the mode at 215~Hz, would require, e.g.,
that a two-pole low-pass filter have its cut-off frequency at about
20~Hz. Thus, while our feedforward scheme slows the $X$-axis down, we
achieve better bandwidth than we would with a simple low-pass filter.

@@

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
\end{align}
The idea behind the RDI is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.

>>>>

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. Second, and more
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_X}{z-1}\right\rceil
\end{equation}
time steps, where $H_X$ is closed-loop transfer function for the
$X$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.

@@

In general, the $X$-axis positioning requirements are more stringent
for both CS and raster scanning. Due to the step inputs the $X$-axis
must track, we have found that compensating hysteresis and creep to be
particular helpful during $\mu$-path scanning. Thus, the $X$-axis
compensator also includes an inverse creep and hysteresis model. The
hysteresis model is a modified Prandtl-Ishlinskii type model and is
based on the work of \cite{kuhnen_modeling_2003}, while the drift
compensation models the piezo creep as a simple second-order transfer
function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the
hysteresis inversion is indicated by $\mathcal{H}_X^{-1}[\cdot]$. We
have found that the inclusion of these extra compensators limits the
overshoot of the $X$-axis during larger moves between different
$\mu$-paths (e.g., without them, the $X$-axis trajectory in
Fig.~\ref{fig:with_ff} would show noticeable overshoot). More details
on fitting the creep and hysteresis models can be found in our other
work \cite{braker_afmmpc_2019}.

@@

In principle, one could mitigate these issues with a full MIMO control
design. In this work, we opt for a much simpler feedforward scheme.
For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in
Fig.~\ref{fig:afm_bd_dinv}) with three notches: at 215~Hz, 350~Hz, and
505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the
dashed-pink curves and the
resulting overall FRF is shown as the blue curves, which show a
dramatic reduction in the cross coupling. A similar effect could be
achieve by using a simple low-pass filter. However, to achieve the
same 40~dB of attenuation of the mode at 215~Hz would require, e.g.,
that a two-pole low-pass filter have its cut-off frequency at about
20~Hz. Thus, while our feedforward scheme slows the $X$-axis down, we
achieve better bandwidth than we would with a simple low-pass filter.

@@

\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}
\end{align}
The idea behind the RDI is that increased scan rates lead to larger
deflection signals (and thereby increased force into the specimen) at
each surface feature, which the RDI accumulates.
